Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2022-01-07 paper.tex
add some figures

Likelihood-based parameter confidence intervals are relatively narrow within
each specified model
(Tables~\ref{tab:supp-single-origin-fits}--\ref{tab:supp-merger-with-stem-migration-fits}),
reflecting an informative statistical approach. As expected, model assumptions
have a larger impact on parameter estimates. To convey model uncertainty, we
highlight features of two models with the highest \aprcomment{not the
highest\ldots merger-without-stem-migration at -107,650}log likelihoods. These
differ primarily in whether early stems are assumed to give rise to modern
populations in multiple discrete merger events or in continuous migrations
\aprcomment{(Figure 2)}. Additional models are discussed in
\aprcomment{Supplement XXX}.

>>>>

Likelihood-based parameter confidence intervals are relatively narrow within
each specified model
(Tables~\ref{tab:supp-single-origin}--\ref{tab:supp-merger-with-stem-migration}),
reflecting an informative statistical approach. As expected, model assumptions
have a larger impact on parameter estimates. To convey model uncertainty, we
highlight features of two models with the highest \aprcomment{not the
highest\ldots merger-without-stem-migration at -107,650}log likelihoods. These
differ primarily in whether early stems are assumed to give rise to modern
populations in multiple discrete merger events or in continuous migrations
\aprcomment{(Figure 2)}. Additional models are discussed in
\aprcomment{Supplement XXX}.

### 2022-01-07 supplement.tex
add some figures

@@

@@

>>>>

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{figures/supp-h12s-all-models.pdf}
    \caption{
        \textbf{Predicted pairwise differentiation between contemporaneous populations.}
        \aprcomment{Plot ordering, line colors and styles, etc need to be cleaned up.
        Add panel labels.}
        All models (A: single origin, B: continuous migration, C: merger without stem
        migration, D: merger with stem migration)\dots
    }
    \label{fig:supp-h12-panels}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{figures/supp-exp-coal-rates}
    \caption{
        \textbf{Expected inverse instantaneous coalescence rates from models.}
    }
    \label{fig:supp-iicr-exp}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.75\textwidth]{figures/supp-relate-rccr-model-exp.pdf}
    \caption{
        \textbf{Expected relative cross-coalescence rates from inferred models.}
    }
    \label{fig:supp-rccr-exp}
\end{figure}
